% Ceyhun Şen's Resume

% Use custom CLS file.
\documentclass[10pt]{brutalist}

% Initials.
\title{Ceyhun Şen Resume}
\author{Ceyhun Şen}
\date{\today}

\input{common.tex}

% Main content -----------------------------------------------------------------
\begin{document}

\contactbox
{Ceyhun Şen}
{ceyhuusen@gmail.com}
{linkedin.com/in/ceyhun-sen}
{github.com/ceyhunsen}

% ------------------------------------------------------------------------------
% Work -------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section*{Work Experience}

\experiencebox
{Chainway Labs}
{
	\href{https://chainway.xyz/}{chainway.xyz} - %
	İstanbul / Türkiye
}
{
	Software Engineer | 03.24 - Today
}
{Rust, Bitcoin, RISC-V Assembly, Low Level Software}
{I work on a state-of-the-art Bitcoin bridge, called Clementine. This work involves developing a high performing software, that is written in Rust. I also worked on a transpiler, which converted RISC-V assembly language to a virtual machine (BitVM).}

\experiencebox
{Inventron Electronics And Software}
{
	\href{https://inventron.com.tr/wp/tr}{inventron.com.tr/wp/tr} - %
	İstanbul / Türkiye
}
{
	Embedded Software Engineer | 09.23 - 03.24\\%
	Part-time Embedded Software Engineer | 02.23 - 08.23\\%
	Embedded Software Intern | 08.22 - 01.23
}
{C, C++, Linux Kernel, U-Boot Bootloader, Yocto Project, Android (kernel and distribution side)}
{I worked on both Linux kernel drivers and board support package development for NXP i.MX based microprocessors and custom SOC's. This work involves writing new or updating existing device drivers/functionalities for various chips and peripherals. All to provide BSP's to complex SOM's and SOC's.}

\experiencebox
{Enterans}
{Bursa / Türkiye}
{
	Part-time Embedded Software Engineer | 03.2022 - 06.2022
}
{C, STM32, ESP8286}
{I worked on writing platform independent peripheral drivers for various microcontrollers in C. Drivers I wrote, used on different microcontrollers.}

% ------------------------------------------------------------------------------
% Education --------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section*{Education}

\begin{itemize}
	\item Bursa Technical University | 08.19 - 08.23 | Computer Engineering Major | GPA: 2.89
	\item Haydarpaşa High School | 09.15 - 06.19
	\item Middle School Mathematical Olympiads | 09.12 - 06.14
\end{itemize}

% ------------------------------------------------------------------------------
% Projects ---------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section*{Projects}

\projectbox
{ATmega328P HAL Driver}
{https://github.com/ceyhunsen/ATmega328P-HAL-Driver}
{
	Hardware abstraction layer driver for ATMega328P microcontroller. Written in C. Includes documentation (Doxygen), unit and integration tests. Tests have a mock interface which can act like real hardware.
}

\projectbox
{MPU-925X Sensor Driver}
{\href{https://github.com/ceyhunsen/mpu925x-driver}{github.com/ceyhunsen/mpu925x-driver}}
{
	Platform independent driver for MPU-9250 and MPU-9255 IMU sensors. Written in C. Includes documentation (Doxygen), unit and integration tests. Tests have a mock interface which can act like real hardware.
}

\projectbox
{BMP180 STM32 Sensor Driver}
{\href{https://github.com/ceyhunsen/bmp180-stm32-driver}{github.com/ceyhunsen/bmp180-stm32-driver}}
{
	Targeted specifically for STM32 microcontrollers and uses STM32 HAL drivers. Written in C.
}

% Skills -----------------------------------------------------------------------
\section*{skills}

\begin{multicols}{2}
\skillbox
{Main Skills}
{
\begin{itemize}
	\item Software development with low level languages like C, C++ and Rust
	\item Embedded software development
	\item Linux driver development
	\item Designing software architecture and writing comprehensive documentation
\end{itemize}
}

\skillbox
{Languages}
{
\begin{itemize}
	\item Turkish | Native
	\item English | Profesional working proficiency
\end{itemize}
}

\skillbox
{Programming Languages}
{C, C++, Rust, Python, Bash, Javascript, CSS, HTML, Java, C\#, \LaTeX}

\skillbox
{Code Libraries And Frameworks}
{Linux driver stack, Rust Tokio, U-Boot driver model, STM32 HAL Drivers, React Native, Jekyll}

\skillbox{Technologies And Platforms}
{Linux Kernel, Bitcoin, Git, GCC, Makefile/CMake, NXP i.MX ARM microprocessors, STM32 microcontrollers, AVR ATMega microcontrollers, Arduino, Inkscape}
\end{multicols}

% ------------------------------------------------------------------------------
% End --------------------------------------------------------------------------
% ------------------------------------------------------------------------------
% Skip to the right end side of the page.
\vfill\null
\hfill\null\footnotesize This document is created/updated at \today.

\end{document}
